### 2023-10-10 main.tex
Update main.tex

Consider two Markov processes $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have 

@@

The duality definition can also be formulated as a relation between the generators. Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$

@@

when the state spaces of the dual processes is finite, the generators and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta^{'})$, $\widetilde{\mathcal{L}}(\xi,\xi^{'})$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta^{'}\in\Omega$ and $\xi,\xi^{'}\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 
    \sum_{\eta^{'}\in\,\Omega}\mathcal{L}(\eta,\eta^{'})D(\eta^{'},\xi)=\sum_{\xi^{'}\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi^{'})D(\eta,\xi^{'})

@@

where the superscript $T$ denotes the matrix transposition. Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}$. Working in terms of the Hamiltonian operators the duality relation \eqref{dualityIntertwines} reads 

@@

\subsection{Duality for the multi-species stirring process}\label{statementDualitySubsection}
In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$, defined by the generator \eqref{Generator}.

@@

This means that to each site $x\in V$ we associate an ``extra-site'', denoted $u(x)$. The configuration space of the dual process is the enlarged state space

@@

    \widetilde{\Omega}= \bigtimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigtimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt

>>>>

Consider two Markov processes, $(\eta_{t})_{t\geq 0}$ defined on a state space $\Omega$ and $(\xi_{t})_{t\geq 0}$ defined on a state space $\widetilde{\Omega}$. We say that they are dual, with respect to a duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$, if $\forall \eta\in\Omega$, $\forall \xi\in\widetilde{\Omega}$ and $\forall t> 0$ we have 

@@

The duality definition can also be formulated as a relation between the generators, provided some minimal technical conditions are satisfied \cite{jansen2014notion}. Call $\mathcal{L}$ the generator of $(\eta_{t})_{t\geq0}$ and $\widetilde{\mathcal{L}}$ the generator of $(\xi_{t})_{t\geq 0}$, then we say that these two processes are dual with respect to the duality function $D:\Omega\times \widetilde{\Omega}\to \mathbb{R}$ if $\forall \eta\in\Omega$ and $\forall \xi\in\widetilde{\Omega}$

@@

when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 
    \sum_{\eta'\in\,\Omega}\mathcal{L}(\eta,\eta')D(\eta',\xi)=\sum_{\xi'\in\, \widetilde{\Omega}}\widetilde{\mathcal{L}}(\xi,\xi')D(\eta,\xi')

@@

where the superscript $T$ denotes the matrix transposition. Therefore, the duality relation \eqref{dualityIntertwines} is an intertwining between two linear operators $\mathcal{L}$ and $\widetilde{\mathcal{L}}^{\,T}$. Working in terms of the Hamiltonian operators the duality relation reads 

@@

\subsection{Duality for the open multi-species stirring process}\label{statementDualitySubsection}
In this section we formulate duality for the multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ with open boundaries, defined by the generator \eqref{Generator}.

@@

This means that to each site $x\in V$ we associate an ``extra-site'' via a bijection $u:V\to V$. We denote as $u(x)$ the extra-site asspciated to $x\in V$ . The configuration space of the dual process is the enlarged state space

@@

    \widetilde{\Omega}= \bigotimes_{x\in V} \widetilde{\Omega}_{x}\ = \bigotimes_{x\in V} (\Omega_{x}\times \mathbb{N}_{0}^{N})\dt
